Complex Geometry - Index of Notations and ideas

### 2016-08-03 Complex Geometry - index/Complex Geometry - index.tex
New complex geometry note.

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{article}

@@

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

@@

\begin{abstract}
Obviously.

\end{abstract}

\section{Book}
	\subsection{1. Local Theory}
		\subsubsection{1.1 Holomorphic Functions of Several Variables}
		\label{sec:1.1_book}
		\textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.

@@

		\textcolor{blue}{1}: 
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}: 
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:
		\textcolor{blue}{1}:

	\subsection{2.Complex Manifolds}

		\subsubsection{2.2 Holomorphic Vector Bundles}

@@

		\subsubsection{2.6 Differential Calculus on Complex Manifolds}

@@

		\textcolor{blue}{$\wedge^{p,q}X$}:=$\wedge^p(T^{1,0}X)^*
							\bigotimes_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)

@@

\section{My lecture Notes}

	\subsection{Lecture 2016 Lecture 1}
	The first few lectures are not well noted, hence I delegate the task of recording the theorems and notations to the book's correspoding section:\fref{sec:1.1_book}.

	\subsection{Lecture 4 (20160307) Complex Manifold}

@@

	\subsection{Lecture 5 Submanifolds (20160308)}

@@

	\subsection{Lecture 6 Sheaf \& Cohomology (20160315)}
	pp. A:
		\begin{itemize}
			\item Stalk $\mathcal{F}_x$.
			\item germ
			\item Directed partial order set
			\item Directed System
		\end{itemize}
	pp. B:
		\begin{itemize}
			\item Directed limit
		\end{itemize}
	pp. C:
	\begin{itemize}
		\item Exact Complex/ Exact Sequence.
		\item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
		\item
	\end{itemize}
	pp. D:
	\begin{itemize}
		\item Čech cohomology
	\end{itemize}
	pp. E:
	\begin{itemize}
		\item q-cochain
		\item coboundary operator. $\delta$.
		\item $Z^p(U,\mathcal{F})$ = Ker.
		\item $B^p(U,\mathcal{F})$ = Im.
		\item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
	\end{itemize}
    \subsubsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
		pp.1:
		\begin{itemize}
			\item q-simplex $\sigma$.
			\item support $|\sigma|$.
			\item q-cocain
			\item $C^q(U,\mathcal{F})$
			\item Coboundary Operator $\delta$.
		\end{itemize}
		pp.2,3,4:
		\begin{itemize}
			\item Cochain Complex
			\item Čech cohomology
			\item cocycle
			\item cochain
			\item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
			\item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
		\end{itemize}

	\subsection{Lecture 7 Vector Bundle (20160321)}
	pp.1,2:
	\begin{itemize}
		\item Vector Bundle
		\item Trivializing covering, $\{(U_i,\tau_i)\}$.
		\item trivializing maps, trivializes.
		\item VB-equivalent of trivializing maps.
		\item E: total space, X: base space.
	\end{itemize}
	pp. 3,5:
	\begin{itemize}
		\item transition maps.
		\item fibre.
		\item $\mathcal{O}(-1)$
		\item cocycle condition.
		\item $\mathcal{T}_X$, Holomorphic tangent bundle.
	\end{itemize}
	pp. 8:
	\begin{itemize}
		\item s: section of a holomorphic vector bundle.
		\item $\mathcal{E}$: sheaf of sections of holomorphic vector bundle. $\mathcal{E}(U)$.
	\end{itemize}

	\subsection{Lecture 8 Almost Complex Structures (20160322)}
	pp. 1,2:
	\begin{itemize}
		\item $I$: Almost Complex Structure. $I^2=-1$. Sometime $J$ is used in place of $I$.
		\item $V_{\mathbb{C}}$ := $V\otimes \mathbb{C}$.
		\item $I_\mathbb{C}$: $I$ extending to $V_{\mathbb{C}}$. Usually abbreviated simply as $I$.
		\item $V^{1,0}$:= ker$(I+i)$.
		\item $V^{0,1}$:= ker$(I-i)$.
	\end{itemize}

	\subsection{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}

@@

	\subsection{Lecture 10 Debeault Cohomology (20160406)}

@@

	\subsection{Lecture 11 (20160412)}
	pp.1,2,3: 
	\begin{itemize}
		\item $\bar{\partial}$-Poincaré lemma in n-dimension
		\item $\Omega_X^p$: holomorphic p-forms. On pp.2.
		\item $\check{H}^q(X,\Omega^p)\text{(Čech)}\cong \mathcal{H}_{\bar{\partial}}^{p,q}(X)$(Dolbeault). On pp.3.
	\end{itemize}
	pp. 6,7:
	\begin{itemize}
		\item Analytic Subvarity.
		\item Analytic Hybersurface.
		\item Cousin's Problem.
	\end{itemize}

	\subsection{Lecture 12 Hermitan Structure on Manifold  Manifold (20160418)}
	pp. 1,2,3:
	\begin{itemize}
		\item $I$ compatible with $<-,->$.
		\item $\omega$: Fundamental form associated with $<,>$ and $I$. $\omega(v,w):= <I(v),w>$.
		\item Conformal Equivalence.
		\item $<,>$: Hermitian Inner Product.
	\end{itemize}
	pp. 4:
	\begin{itemize}
		\item $( , )$: s.t. $(v,w):=<v,w>-i\omega(v,w) = <v,w> - i <I(v),w>$
	\end{itemize}
	pp. 5:
	\begin{itemize}
		\item $<,>_{\mathbb{C}}$ be s.t.$<v\otimes \alpha, w\otimes \beta>:= \alpha \bar{\beta} <v,w>$.
	\end{itemize}
	pp. 6:
	\begin{itemize}
		\item $\frac{1}{2}(,) = <,>_{\mathbb{C}} \arrowvert_{V^{1,0}}$
	\end{itemize}
	pp. 7,8:
	\begin{itemize}
		\item Local computations: $z_i$,$h_{ij}$,
		\item $\omega = (...dx^i...dy^i)$
		\item $\omega$, Fundamental form on Riemannian Mnfd.
		\item Kähler mnfd: $d\omega \equiv 0$.
	\end{itemize}

	\subsection{Lecture 13 Kähler Manifold (20160419)}
	pp.1:
	\begin{itemize}
		\item Local computation: $\omega = (...dz^i...d\bar{z}^i)$
	\end{itemize}
	pp.4:
	\begin{itemize}
		\item Fubini-Study Metric on $\mathbb{CP}^n$.
	\end{itemize}

	\subsection{Lecture 14 Hodge Theory (20160425)}
	pp.1:
	\begin{itemize}
		\item $<,>$ on $\Lambda^k V$
		\item vol: volumn element.
		\item $*$: Hodge Star Operator.
	\end{itemize}
	pp.4:
	\begin{itemize}
		\item $L$: Lefschetz Operator
		\item $\Lambda$: adjoint of $L$. $\Lambda = *^{-1}\circ L\circ *$.
	\end{itemize}
	pp.5 :
	\begin{itemize}
		\item $*,L,\Lambda$ on Kähler mnfd.
		\item $d^*:= (-1)^{m*(k+1)+1}*\circ d\circ*$, adjoint of $d$. On a Kähler mnfd, $d^*= -*\circ d\circ*$
		\item $\Delta:=d^*\circ d + d\circ d^*$.
	\end{itemize}
	pp. 6:
	\begin{itemize}
		\item $\bar{\partial}^*, \partial^*$: Similar to the above for $d$.
		\item $\Delta_\partial, \Delta_{\bar{\partial}}$: Similar to the above for $d$.
	\end{itemize}

	\subsection{Lecture 15 Hodge Theory on Manifold (20160426)}
	pp.1:
	\begin{itemize}
		\item $(,)$ on $\mathcal{A}^*(X)$. $(\alpha,\beta):=\int_X g_\mathbb{C}(\alpha,\beta) vol$
	\end{itemize}
	pp.3:
	\begin{itemize}
		\item $\mathcal{H}^k(X,g)$: d-harmonic forms. Sometimes we replace $\mathcal{H}$ with $\mathscr{H}$ for harmonic forms, so is for symbols below.
		\item $\mathcal{H}^k_{\bar{\partial}}(X,g)$: $\bar{\partial}$-harmonic forms. 
		(Be careful to distinguish this with Dolbeault Cohomology groups).
		\item $\mathcal{H}^k_{\partial}(X,g)$: $\partial$-harmonic forms.
	\end{itemize}
	pp. 5:
	\begin{itemize}
		\item $\mathcal{H}^k_d(X,g) \cong \mathcal{H}^{2n-k}_d(X,g)$, Poincar\'{e} duality
		\item $\mathcal{H}^{p,q}_{\bar{\partial}}(X,g) \cong 
		\left( \mathcal{H}^{n-p,n-q}_{\bar{\partial}}(X,g)\right)^*$, both are harmonic forms, called Serre Duality. 
	\end{itemize}
	pp. 6,7:
	\begin{itemize}
		\item 
		$\mathcal{A}^{p,q} = 
		\bar{\partial}\mathcal{A}^{p,q-1}(X)\oplus
		\bar{\partial}^* \mathcal{A}^{p,q+1}(X) \oplus
		\mathcal{H}^{p,q}_{\bar{\partial}}(X,g)$:

@@

	\subsection{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}

@@

	\subsection{Lecture 17 Hermitian Vector Bundle (20160510)}
	pp.1,3:
	\begin{itemize}
		\item Hermitian Vector Bundle. pp.1
		\item Antilinear map. pp.3.
		\item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
		\item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
		\item $\bar{\partial}_E^*$
	\end{itemize}
	pp. 8:
	\begin{itemize}
		\item Kadaira-Serre Duality.
	\end{itemize}

	\subsection{Lecture 18 Connection (20160516)}
	\begin{itemize}
		\item $\bigtriangledown$: connection. pp.1.
		\item Trivial connections. pp.2
		\item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
		\item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
		\item $\Delta = d+A$. pp.4.
		\item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
		\item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
		\item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
	\end{itemize}

	\subsection{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
	\begin{itemize}
		\item Holomorphic Connecction. pp.1.
		\item $At(E)$: Atiyah class of $E$. pp.2.
		\item $\Delta^k$. pp.4.
		\item $F_\Delta$: curvature associated with $\Delta$. pp.5.
		\item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
		\item First Chern class of complex line bundle.
	\end{itemize}

	\subsection{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
	\begin{itemize}
		\item Analytic Subvariety. pp.1.
		\item Regular/Smooth Point. pp.1.
		\item Singular Point. pp.2.
		\item Irreducible analytic subvariety. pp.2.
		\item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
		\item Affine algebraic varieties. pp.3.
		\item Projective algebraic varieties. pp.3.
		\item Hypersurface. pp.4.
		\item Divisor, $Div(X)$:=group of all divisors. pp.5.
		\item Effective divisor. pp.6.
		\item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
		\item Meromorphic function on complex mnfd.
		\item $(f)$: divisor given by a global meromorphic function.
		\item Principal divisor. pp.8.
	\end{itemize}

	\subsection{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
	\begin{itemize}
		\item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
		\item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
		\item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
		\item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
		\item Linear equivalent of divisors.
		\item $*$: used only in this section to denoted the map:
		$$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
		pp.6.
		\item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
	\end{itemize}

	\subsection{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
	\begin{itemize}
		\item Base point of a line bundle. pp.4.
		\item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
		\item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
	\end{itemize}

\begin{thebibliography}{1}

	\bibitem{blog} Complex Geometry

\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

% The entire content of this work (including the source code
% for TeX files and the generated PDF documents) by 
% Hongxiang Chen (nicknamed we.taper, or just Taper) is
% licensed under a 
% Creative Commons Attribution-NonCommercial-ShareAlike 4.0 
% International License (Link to the complete license text:
% http://creativecommons.org/licenses/by-nc-sa/4.0/).
\documentclass{book}

@@

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

@@

\part{Indices of Notation}

\chapter{Book}
\section{1. Local Theory}
    \subsection{1.1 Holomorphic Functions of Several Variables}
    \label{sec:1.1_book}
    \textbf{Note}: the content covered by this seciton is geared for accompanying my personal notes of lecture 1.

@@

    \textcolor{blue}{germ of set}: (\textbf{pp.18})

    \textcolor{blue}{$Z(f)$}: germ of zero set of $f$. (\textbf{pp.18})

    \textcolor{blue}{analytic germ}: $Z(f_1,\cdots,f_k)$. (\textbf{pp.18})

    \textcolor{blue}{analytic subset}: locally are zero sets. (\textbf{pp.18})

    \textcolor{blue}{$I(X)$}: the set of all $f\in
    \mathcal{O}_{\mathbb{C}^n,0}$ with $X\subset Z(f)$. (\textbf{pp.18})
    % TODO bookmark
    \subsection{1.2 Complex and Hermitian Structures}
    \textcolor{blue}{almost complex structure, $I$}: $I^2=-\text{id}$.
    (\textbf{pp.25})

    \textcolor{blue}{$V^{1,0}$ and $V^{0,1}$}: the $\pm i$ eigenspaces 
    of $I$.
    (\textbf{pp.25})

    \textcolor{blue}{$\bigwedge^{p,q} V$}:=
    $\bigwedge^p V^{1,0}\oplus_{\mathbb{C}}\bigwedge^q V^{0,1}$.
    (\textbf{pp.27})

    \textcolor{blue}{$\prod^k,\prod^{p,q}$}: natural projections.
    (\textbf{pp.28})

    \textcolor{blue}{$\mathbf{I}$}:=$\sum_{p,q}i^{p-q}\cdot\prod^{q,p}$.
    (\textbf{pp.28})

    \textcolor{blue}{compatible}:an almost complex structure $I$ is
    compatible with the scalar product $<,>$, if $<I(v),I(w)>=<v,w>$.
    (\textbf{pp.28})

    \textcolor{blue}{Conformal equivalence}(between scalar product):
    (\textbf{pp.29})

    \textcolor{blue}{fundamental form, $\omega$}:=$<I\text{( )},()>.$
    (\textbf{pp.29})
    $$\omega=\frac{i}{2}\sum_i z^i\wedge\bar{z}^i=\sum_i x^i\wedge y^i.$$
    \quad(Local calculation could be found on \textbf{pp.31})

    \textcolor{blue}{hermitian form $(,)$}:=$<,>-i\cdot\omega$.
    (\textbf{pp.30})
\section{2.Complex Manifolds}

    \subsection{2.1 Complex and Hermitian Structures}
    \textcolor{blue}{almost complex structure}: (\textbf{pp.25})
	\subsection{2.2 Holomorphic Vector Bundles}

@@

    \subsection{2.6 Differential Calculus on Complex Manifolds}

@@

    \textcolor{blue}{$\wedge^{p,q}X$}:=$\wedge^p(T^{1,0}X)^*
                        \bigoplus_{\mathbb{C}}\wedge^q(T^{0,1}X)^*$. (Def 2.6.7 at pp. 105)

@@

\chapter{My lecture Notes}

\section{Lecture 2016 Lecture 1}
The first few lectures are not well noted, hence I delegate the task of recording the theorems and notations to the book's correspoding section:\fref{sec:1.1_book}.

\section{Lecture 4 (20160307) Complex Manifold}

@@

\section{Lecture 5 Submanifolds (20160308)}

@@

\section{Lecture 6 Sheaf \& Cohomology (20160315)} pp. A:
    \begin{itemize}
        \item Stalk $\mathcal{F}_x$.
        \item germ
        \item Directed partial order set
        \item Directed System
    \end{itemize}
pp. B:
    \begin{itemize}
        \item Directed limit
    \end{itemize}
pp. C:
\begin{itemize}
    \item Exact Complex/ Exact Sequence.
    \item Exponential sequence \textit{(mentioned under the definition of exact sequence)}.
    \item
\end{itemize}
pp. D:
\begin{itemize}
    \item Čech cohomology
\end{itemize}
pp. E:
\begin{itemize}
    \item q-cochain
    \item coboundary operator. $\delta$.
    \item $Z^p(U,\mathcal{F})$ = Ker.
    \item $B^p(U,\mathcal{F})$ = Im.
    \item $\check{H}^p(U,\mathcal{F})$ = $\frac{Ker}{Im}$.
\end{itemize}

    \subsection{Notes of \v{C}ech Cohomology with Coeficients in a Sheaf}
    pp.1:
    \begin{itemize}
        \item q-simplex $\sigma$.
        \item support $|\sigma|$.
        \item q-cocain
        \item $C^q(U,\mathcal{F})$
        \item Coboundary Operator $\delta$.
    \end{itemize}
    pp.2,3,4:
    \begin{itemize}
        \item Cochain Complex
        \item Čech cohomology
        \item cocycle
        \item cochain
        \item $\check{H}^p(U,\mathcal{F}),Z^p(U,\mathcal{F}),B^p(U,\mathbb{F})$.
        \item $\check{H}^0(\{u_i\},\mathcal{F})$ = $\mathcal{F}(X)$.
    \end{itemize}

\section{Lecture 7 Vector Bundle (20160321)}
pp.1,2:
\begin{itemize}
    \item Vector Bundle
    \item Trivializing covering, $\{(U_i,\tau_i)\}$.
    \item trivializing maps, trivializes.
    \item VB-equivalent of trivializing maps.
    \item E: total space, X: base space.
\end{itemize}
pp. 3,5:
\begin{itemize}
    \item transition maps.
    \item fibre.
    \item $\mathcal{O}(-1)$
    \item cocycle condition.
    \item $\mathcal{T}_X$, Holomorphic tangent bundle.
\end{itemize}
pp. 8:
\begin{itemize}
    \item s: section of a holomorphic vector bundle.
    \item $\mathcal{E}$: sheaf of sections of holomorphic vector bundle. $\mathcal{E}(U)$.
\end{itemize}

\section{Lecture 8 Almost Complex Structures (20160322)}
pp. 1,2:
\begin{itemize}
    \item $I$: Almost Complex Structure. $I^2=-1$. Sometime $J$ is used in place of $I$.
    \item $V_{\mathbb{C}}$ := $V\otimes \mathbb{C}$.
    \item $I_\mathbb{C}$: $I$ extending to $V_{\mathbb{C}}$. Usually abbreviated simply as $I$.
    \item $V^{1,0}$:= ker$(I+i)$.
    \item $V^{0,1}$:= ker$(I-i)$.
\end{itemize}

\section{Lecture 9 Exterior Algebra on Complex Manifold (20160329)}

@@

\section{Lecture 10 Debeault Cohomology (20160406)}

@@

\section{Lecture 11 (20160412)}
pp.1,2,3: 
\begin{itemize}
    \item $\bar{\partial}$-Poincaré lemma in n-dimension
    \item $\Omega_X^p$: holomorphic p-forms. On pp.2.
    \item $\check{H}^q(X,\Omega^p)\text{(Čech)}\cong \mathcal{H}_{\bar{\partial}}^{p,q}(X)$(Dolbeault). On pp.3.
\end{itemize}
pp. 6,7:
\begin{itemize}
    \item Analytic Subvarity.
    \item Analytic Hybersurface.
    \item Cousin's Problem.
\end{itemize}

\section{Lecture 12 Hermitian Structure on Manifold  Manifold (20160418)}
pp. 1,2,3:
\begin{itemize}
    \item $I$ compatible with $<-,->$.
    \item $\omega$: Fundamental form associated with $<,>$ and $I$. $\omega(v,w):= <I(v),w>$.
    \item Conformal Equivalence.
    \item $<,>$: Hermitian Inner Product.
\end{itemize}
pp. 4:
\begin{itemize}
    \item $( , )$: s.t. $(v,w):=<v,w>-i\omega(v,w) = <v,w> - i <I(v),w>$
\end{itemize}
pp. 5:
\begin{itemize}
    \item $<,>_{\mathbb{C}}$ be s.t.$<v\otimes \alpha, w\otimes \beta>:= \alpha \bar{\beta} <v,w>$.
\end{itemize}
pp. 6:
\begin{itemize}
    \item $\frac{1}{2}(,) = <,>_{\mathbb{C}} \arrowvert_{V^{1,0}}$
\end{itemize}
pp. 7,8:
\begin{itemize}
    \item Local computations: $z_i$,$h_{ij}$,
    \item $\omega = (...dx^i...dy^i)$
    \item $\omega$, Fundamental form on Riemannian Mnfd.
    \item Kähler mnfd: $d\omega \equiv 0$.
\end{itemize}

\section{Lecture 13 Kähler Manifold (20160419)}
pp.1:
\begin{itemize}
    \item Local computation: $\omega = (...dz^i...d\bar{z}^i)$
\end{itemize}
pp.4:
\begin{itemize}
    \item Fubini-Study Metric on $\mathbb{CP}^n$.
\end{itemize}

\section{Lecture 14 Hodge Theory (20160425)}
pp.1:
\begin{itemize}
    \item $<,>$ on $\Lambda^k V$
    \item vol: volumn element.
    \item $*$: Hodge Star Operator.
\end{itemize}
pp.4:
\begin{itemize}
    \item $L$: Lefschetz Operator
    \item $\Lambda$: adjoint of $L$. $\Lambda = *^{-1}\circ L\circ *$.
\end{itemize}
pp.5 :
\begin{itemize}
    \item $*,L,\Lambda$ on Kähler mnfd.
    \item $d^*:= (-1)^{m*(k+1)+1}*\circ d\circ*$, adjoint of $d$. On a Kähler mnfd, $d^*= -*\circ d\circ*$
    \item $\Delta:=d^*\circ d + d\circ d^*$.
\end{itemize}
pp. 6:
\begin{itemize}
    \item $\bar{\partial}^*, \partial^*$: Similar to the above for $d$.
    \item $\Delta_\partial, \Delta_{\bar{\partial}}$: Similar to the above for $d$.
\end{itemize}

\section{Lecture 15 Hodge Theory on Manifold (20160426)}
pp.1:
\begin{itemize}
    \item $(,)$ on $\mathcal{A}^*(X)$. $(\alpha,\beta):=\int_X g_\mathbb{C}(\alpha,\beta) vol$
\end{itemize}
pp.3:
\begin{itemize}
    \item $\mathcal{H}^k(X,g)$: d-harmonic forms. Sometimes we replace $\mathcal{H}$ with $\mathscr{H}$ for harmonic forms, so is for symbols below.
    \item $\mathcal{H}^k_{\bar{\partial}}(X,g)$: $\bar{\partial}$-harmonic forms. 
    (Be careful to distinguish this with Dolbeault Cohomology groups).
    \item $\mathcal{H}^k_{\partial}(X,g)$: $\partial$-harmonic forms.
\end{itemize}
pp. 5:
\begin{itemize}
    \item $\mathcal{H}^k_d(X,g) \cong \mathcal{H}^{2n-k}_d(X,g)$, Poincar\'{e} duality
    \item $\mathcal{H}^{p,q}_{\bar{\partial}}(X,g) \cong 
    \left( \mathcal{H}^{n-p,n-q}_{\bar{\partial}}(X,g)\right)^*$, both are harmonic forms, called Serre Duality. 
\end{itemize}
pp. 6,7:
\begin{itemize}
    \item 
    $\mathcal{A}^{p,q} = 
    \bar{\partial}\mathcal{A}^{p,q-1}(X)\oplus
    \bar{\partial}^* \mathcal{A}^{p,q+1}(X) \oplus
    \mathcal{H}^{p,q}_{\bar{\partial}}(X,g)$:

@@

\section{Lecture 16 Harmonic forms on K\"{a}hler Manifold (20160503)}

@@

\section{Lecture 17 Hermitian Vector Bundle (20160510)}
pp.1,3:
\begin{itemize}
    \item Hermitian Vector Bundle. pp.1
    \item Antilinear map. pp.3.
    \item Hermitian Inner Product on $\mathcal{A}^{p,q}(X,E)$. pp.4
    \item $\bar{*}_E$ Hodge Operator on Hermitian vector bundle. pp.5.
    \item $\bar{\partial}_E^*$
\end{itemize}
pp. 8:
\begin{itemize}
    \item Kadaira-Serre Duality.
\end{itemize}

\section{Lecture 18 Connection (20160516)}
\begin{itemize}
    \item $\bigtriangledown$: connection. pp.1.
    \item Trivial connections. pp.2
    \item $\mathcal{A}^1(M,End(E)):=\Gamma(M,\Lambda^1 M\otimes End(E))$. pp.3. Also, one may find how elements in this sheaf act on $\mathcal{A}^0(M)$ on pp.173, inside proof of proposition 4.2.3.
    \item $s\in \mathcal{A}^0(E)$ is Parrallel/flat/constant $\Leftrightarrow \Delta(s) = 0$. pp.4.
    \item $\Delta = d+A$. pp.4.
    \item $\Delta$ be compatible with hermitian structure on $E$. pp.5.
    \item $\Delta$ be compatible with holomorphic vector bundle. pp.6.
    \item $A=\bar{H}^{-1} \partial H$. Chern connection. pp.6.
\end{itemize}

\section{Lecture 19 Holomorphic Connection \& Curvature(20160517)}
\begin{itemize}
    \item Holomorphic Connecction. pp.1.
    \item $At(E)$: Atiyah class of $E$. pp.2.
    \item $\Delta^k$. pp.4.
    \item $F_\Delta$: curvature associated with $\Delta$. pp.5.
    \item $F_\Delta = dA + A\wedge A$: Cartan structure equation. pp.6.
    \item First Chern class of complex line bundle.
\end{itemize}

\section{Lecture 20 Divisors \& (Holomorphic) Line Bundles (20160524)}
\begin{itemize}
    \item Analytic Subvariety. pp.1.
    \item Regular/Smooth Point. pp.1.
    \item Singular Point. pp.2.
    \item Irreducible analytic subvariety. pp.2.
    \item $dim(Y)$: dimension of analytic subvariety. pp.2. Also pp.4.
    \item Affine algebraic varieties. pp.3.
    \item Projective algebraic varieties. pp.3.
    \item Hypersurface. pp.4.
    \item Divisor, $Div(X)$:=group of all divisors. pp.5.
    \item Effective divisor. pp.6.
    \item $Ord_Y(f)$: order of function. pp.6. Also pp.8.
    \item Meromorphic function on complex mnfd.
    \item $(f)$: divisor given by a global meromorphic function.
    \item Principal divisor. pp.8.
\end{itemize}

\section{Lecture 21 Divisors \& (Holomorphic) Line Bundles  (20160530)}
\begin{itemize}
    \item $H^0(X,K^*_X/\mathcal{O}^*_X) \cong Div(X)$. pp.1.
    \item $Pic(X)$: Picard group, all holomorphic line bundles. pp.3.
    \item $Pic(X) \cong \check{H}^1(X,\mathcal{O}^*_X)$. pp.3.
    \item $\mathcal{O}(D)$: line bundle given by divisor $D$. pp.5.
    \item Linear equivalent of divisors.
    \item $*$: used only in this section to denoted the map:
    $$\left( Div(X)/Pic(X) \right) \hookrightarrow Pic(X)$$
    pp.6.
    \item $Z(s)$: divisor constructed from nonzero section $s\in H^0(X,L)$ for a line bundle $L$.
\end{itemize}

\section{Lecture 22 Divisors \& (Holomorphic) Line Bundles (20160606)}
\begin{itemize}
    \item Base point of a line bundle. pp.4.
    \item $Bs(L)$:= set of all base points of line bundle $L$. pp.4.
    \item $\mathcal{O}(1), \mathcal{O}(k)$. pp.6.
\end{itemize}

\part{Indices of Results}

{Theorems, Remarks, etc.}
\chapter{Local Theory}
\label{chap:Local Theory}

\section{1.1 Holomorphic Functions of Several Variables}
\label{sec:book_1.1}

\begin{prop}
    The local ring $\mathcal{O}_{\mathbb{C}^n,0}$ is a UFD.
\end{prop}
(\textbf{pp.14 of \cite{book}})

\begin{prop}{Weierstrass division theorem}
    Let $f\in \mathcal{O}_{\mathbb{C}^n,0}$ and $g\in
    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ be a Weierstrass
    polynomial of degree $d$. Then there exist $r\in
    \mathcal{O}_{\mathbb{C}^{n-1},0}[z_1]$ of degree $<d$
    and $h\in \mathcal{O}_{\mathbb{C}^n,0}$ such that $f=g\cdot h+r$.
    The functions $h$ and $r$ are uniquely determined.
\end{prop}
(\textbf{pp.15 of \cite{book}})

\begin{prop}
    The local UFT $\mathcal{O}_{\mathbb{C}^n,0}$ is Noetherian.
\end{prop}
(\textbf{pp.16 of \cite{book}})

\begin{coro}
    Let $g\in \mathcal{O}_{\mathbb{C}^n,0}$ be an irreducible function.
    If $f\in\mathcal{O}_{\mathbb{C}^n,0}$ vanishes on $Z(g)$, then
    $g$ divides $f$.
\end{coro}
(\textbf{pp.16 of \cite{book}})

\begin{lemma}
    For any germ $X\subset \mathbb{C}^n$ the set $I(X)\subset
    \mathcal{O}_{\mathbb{C}^n,0}$ is an ideal.
    If $(A)\subset \mathcal{O}_{\mathbb{C}^n,0}$ denotes the ideal
    generated by the subset $A\subset \mathcal{O}_{\mathbb{C}^n,0}$,
    then $Z(A)=Z((A))$ and $Z(A)$ is analytic.
\end{lemma}
(\textbf{pp.18 of \cite{book}})

\begin{lemma}
    If $X_1\subset X_2$, then $I(X_2)\subset I(X_1)$. If $I_1\subset I_2$,
    then $Z(I_2)\subset Z(I_1)4$. For any analytic germ $X$ one has
    $Z(I(X))=X$. For any ideal $I\subset \mathcal{O}_{\mathbb{C}^n,0}$,
    one has $I\subset I(Z(I))$.
\end{lemma}
(\textbf{pp.18 of \cite{book}})
% TODO bookmark this chapter stops at page 18.

\section{1.2 Complex and Hermitian Structures}
\begin{lemma}
    If $I$ is an almost complex structure on a real vector space $V$,
    then $V$ admits in a natural way the structure of a complex vector
    space
\end{lemma}
(\textbf{pp.25 of \cite{book}})

\begin{remark}
    An almost complex structure can only exist on an even dimensional
    real vector space.
\end{remark}

\begin{coro}
    Any almost complex structure on $V$ induces a natural orientation
    on $V$.
\end{coro}
(\textbf{pp.25 of \cite{book}})

\begin{lemma}
    Let $V$ be a real vector space endowed with an almost complex
    structure $I$. Then
    $$ V_{\mathbb{C}} = V^{1,0}\oplus V^{0,1}$$
    Complex conjugation on $V_{\mathbb{C}}$ induces an $\mathbb{R}$-linear
    isomorphism $V^{1,0}\cong V^{0,1}$.
\end{lemma}
(\textbf{pp.26 of \cite{book}})

\begin{remark}
    Two almost complex structures on $V_{\mathbb{C}}$: $I$ and $i$,
    coincide on the subspace $V^{1,0}$ but differ by a sign on
    $V^{0,1}$.
\end{remark}
